### 2012-12-11 inst/examples/may79-example.Rmd
GP that results in scorched earth fishing strategy

```{r libraries}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
library(kernlab)
```

@@

@@

@@

Parameter definitions

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
gp <- gp_fit(obs, X, c(sigma_n=.9, tau = 1., l=.1), "kernlab")

```

@@

```{r}
df <- data.frame(x=X, y=gp$Ef, ymin=(gp$Ef-2*sqrt(abs(diag(gp$Cf)))), ymax=(gp$Ef+2*sqrt(abs(diag(gp$Cf)))))
true <- data.frame(x=X, y=sapply(X,f, 0, p))
ggplot(df)  + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x,y)) + geom_point(data=obs, aes(x,y)) +
  geom_line(data=true, aes(x,y), col='red', lty=2)
```

@@

```{r}
matrices_gp <- gp_transition_matrix(gp)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

>>>>

```{r libraries}
library(pdgControl)
library(nonparametricbayes)
library(reshape2)
library(ggplot2)
library(data.table)
library(kernlab)
library(tgp)
```

@@

State-space model

@@

Parameters

@@

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
```

@@

```{r}
gp <- bgp(X=obs$x, XX=X, Z=obs$y, verb=0,
          meanfn="linear", bprior="b0", BTE=c(2000,6000,2), m0r1=FALSE, 
          corr="exp", trace=TRUE, beta = c(0,0),
          s2.p = c(50,50), d.p = c(10, 1/0.01, 10, 1/0.01), nug.p = c(10, 1/0.01, 10, 1/0.01),
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", 
          tau2.lam = "fixed", tau2.p = c(50,1))
```

Extract the posterior Gaussian process mean and the $\pm 2$ standard deviations over the predicted grid from the fit:

```{r}
V <- gp$ZZ.ks2
Ef = gp$ZZ.km
tgp_dat <- data.frame(x   = gp$XX[[1]], 
                  y   = gp$ZZ.km, 
                 ymin = gp$ZZ.km - 1.96 * sqrt(gp$ZZ.ks2), 
                 ymax = gp$ZZ.km + 1.96 * sqrt(gp$ZZ.ks2))
```

```{r}
true <- data.frame(x=X, y=sapply(X,f, 0, p))
ggplot(tgp_dat)  + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x,y)) + geom_point(data=obs, aes(x,y)) +
  geom_line(data=true, aes(x,y), col='red', lty=2)
```

@@

```{r}
matrices_gp <- gp_transition_matrix(Ef, sqrt(V), x_grid, h_grid)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```
